FOOBAR: Web-based Data Analytics in Haskell

### 2011-12-15 paper/paper.tex
Copied some of the content from the presentation to the paper

@@

Generate mapreduce queries.

\begin{figure}[]
\begin{verbatim}
    some query goes here
    filler
    filler
    filler
\end{verbatim}
    \caption{Query API}
    \label{api}
\end{figure}

@@

\subsection{League of Legends Data}

@@

@@

There is still lots of work that we could do with our project.

Our project has the limitations A, B, and C.

We could do X.

We could do Y.

Maybe even Z.

>>>>

\begin{figure}[]
\begin{verbatim}
getGameIndexR :: Handler RepHtml
getGameIndexR = do
  (games, opts) <- paginateSelectList 10 [] []
  defaultLayout $ do
    let list = $(widgetFile "game/list")
    setTitle "Game Index"
    toWidget [cassius|
      ##header {
        float: left;
        color = #{color}}
    |] 
    $(widgetFile "game/index")
\end{verbatim}
    \caption{Sample Yesod Controller}
    \label{controller}
\end{figure}

\begin{figure}[]
\begin{verbatim}
^{pager opts}

<table.game-list>
<thead>
  <tr>
    <th>
      Teams
    <th>
      Queue
    <th>
      Date Added
<tbody>
  $forall game <- games
    <tr data-href=@{GameViewR (fst game)}>
      <td.champs>
        ^{portraits champions (snd game)}
      <td.queueType>
        #{gsqueueType (gameGameStats (snd game))}
      <td.created>
        #{gameFormattedCreateTime (snd game)}
\end{verbatim}
    \caption{Sample Hamlet File}
    \label{hamlet}
\end{figure}

@@

Generate mapreduce queries. See figure \ref{mrapi}.

\begin{figure*}[t]
\begin{verbatim}
type Game = GameGeneric backend
type GameId = Key backend Game
GameCreated :: EntityField Game UTCTime
GameGameStats :: EntityField Game GameStats

selectList :: (PersistEntity val, PersistBackend b m) => [Filter val] ->
              [SelectOpt val] -> b m [(Key b val, val)]
selectList [GameCreated <. time] [LimitTo 10] :: PersistBackend b m => b m [(GameId, Game)]
\end{verbatim}
    \caption{Query stuff}
    \label{querycode}
\end{figure*}

\begin{figure*}[t]
\begin{verbatim}
mapReduce :: (PersistBackend Action m, Applicative m, Queryable model)
  => QueryColumn model typ                 -- ^ The column to use a key.
  -> [QueryFilter model]                   -- ^ A list of filters.
  -> forall typ0. [QueryColumn model typ0] -- ^ A list of columns to select for the output.
  -> Action m [(Label, M.Map Label Value)]
\end{verbatim}
    \caption{MapReduce API}
    \label{mrapi}
\end{figure*}

@@

\subsection{League of Legends Logs}

\begin{figure}[]
\begin{verbatim}
parseActionScript :: Parser ByteString ASValue
\end{verbatim}
    \caption{ActionScript parser API}
    \label{asapi}
\end{figure}

@@

Figure \ref{asapi} shows the API.

\subsection{League of Legends Client}

@@

What would be needed to bring this site to a production level?

* More work!

* Static file handling.  Yesod is not optimized for it.

* Load balancing and clustering.

* User accouts/permissions.  Fortunately most of this work has already been done.
